Summary Tables

### 2019-12-19 summary_tables.Rmd
Regen with new props - fixed for capetown

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 83.5|28.8|1.8 |
| bicycle | 2.0|5.8|4.7 |
| car | 2.0|10.7|16.8 |
| motorcycle | 5.6|23.3|20.7 |
| bus | 1.2|18.2|39.1 |

@@

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 92.4|29.7|0.3 |
| bicycle | 1.5|10.5|2.5 |
| car | 5.4|42.3|27.4 |
| motorcycle | 0.0|0.6|0.7 |
| bus | 0.0|3.1|36.0 |

@@

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.1|38.1|0.3 |
| bicycle | 0.8|7.7|1.3 |
| car | 2.3|23.9|28.7 |
| motorcycle | 0.0|3.3|1.9 |
| bus | 0.3|19.0|48.3 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 94.9|54.5|4.2 |
| bicycle | 2.1|14.3|6.2 |
| car | 1.1|10.3|18.9 |
| motorcycle | 0.0|0.0|0.1 |
| bus | 1.4|17.6|65.7 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 70.8|23.9|2.3 |
| bicycle | 0.0|0.5|0.4 |
| car | 7.5|47.2|54.6 |
| motorcycle | 0.0|0.3|0.7 |
| bus | 1.6|28.1|42.1 |

>>>>

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 84.3|11.1|0.8 |
| bicycle | 1.9|7.9|3.6 |
| car | 1.9|14.7|19.6 |
| motorcycle | 5.6|31.9|25.3 |
| bus | 0.7|19.7|35.5 |

@@

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 92.5|29.7|0.3 |
| bicycle | 1.5|10.5|2.5 |
| car | 5.4|42.3|27.4 |
| motorcycle | 0.0|0.6|0.7 |
| bus | 0.0|3.1|36.0 |

@@

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.4|38.1|0.3 |
| bicycle | 0.8|7.7|1.3 |
| car | 2.3|23.9|28.6 |
| motorcycle | 0.0|3.3|1.9 |
| bus | 0.3|19.0|48.2 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 90.0|27.3|2.4 |
| bicycle | 4.5|15.1|4.2 |
| car | 1.4|13.3|18.7 |
| motorcycle | 0.4|5.6|7.2 |
| bus | 3.2|34.1|62.9 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 88.5|23.3|2.0 |
| bicycle | 0.0|0.4|0.3 |
| car | 9.4|46.1|47.3 |
| motorcycle | 0.0|0.3|0.6 |
| bus | 2.0|27.5|36.5 |
